Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-19 main.Rmd
normalisation results look like it is not normalised

```{r norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
mmpd_norm = read_rds("../hakear-drake/data/data_norm_213045f.rds") 
hist_plot = mmpd_norm %>% 
      ggplot() +
      geom_histogram(aes(x = raw_mmpd)) +
      facet_grid(nx~nfacet)
hist_plot
```

```{r null-dist, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2). The distribution of MMPD is unaffected by the null distribution considered. It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
# all_files
# 
# read_files = lapply(all_files, function(x){
#   read_rds(paste0("../hakear-drake/data/", x))
# })
# 
# names(read_files) = str_remove(all_files, pattern = ".rds")
# 
# null_all = bind_rows(normal = read_files$null_normal,
#                      exponential = read_files$null_exp,
#                      gamma = read_files$null_gamma,
#                      weibull = read_files$null_weibull,
#                      .id = "distribution")
# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
design_all = readr::read_rds("data/design_all.rds")

>>>>

```{r norm-data, fig.cap = "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked." }
mmpd_norm = read_rds("../hakear-drake/data/data_norm_213045f.rds") 
hist_plot = mmpd_norm %>% 
      ggplot() +
      geom_histogram(aes(x = raw_mmpd)) +
      facet_grid(nx~nfacet)
hist_plot
```

```{r null-dist, eval =  FALSE, echo = FALSE, fig.cap="Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2). The distribution of MMPD is unaffected by the null distribution considered. It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis."}
# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
# all_files
# 
# read_files = lapply(all_files, function(x){
#   read_rds(paste0("../hakear-drake/data/", x))
# })
# 
# names(read_files) = str_remove(all_files, pattern = ".rds")
# 
# null_all = bind_rows(normal = read_files$null_normal,
#                      exponential = read_files$null_exp,
#                      gamma = read_files$null_gamma,
#                      weibull = read_files$null_weibull,
#                      .id = "distribution")
# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
design_all = readr::read_rds("data/design_all.rds")
